---
title: "01.5_time_to_delay_2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(broom)
library(dplyr)
library(splines)
library(purrr)
library(tidyr)
library(sandwich)
library(emmeans)
library(ggplot2)
library(fixest)
library(tidyr)
library(patchwork)
library(scales)
library(kableExtra)
library(stargazer)
library(lme4)
library(broom.mixed)  # For tidying lmer output
library(lmerTest)
library(knitr)
source('~/afc-claire/code/analysis/00_partisan_difference_functions.R')
```

Children with complete sex and urban/rural classification data
```{r}
data_count = read_csv(paste0('/share/pi/deho-pi/AFC/mortonc/processed/child_politics_covariates_01202026_2018.csv.zip'))
data_count$birth_year = as.numeric(substr(data_count$dob, 1, 4))
data_count <- data_count %>%
  filter(gender != "Other/Unknown" &
         urban_rural != "Unknown" &
           !is.na(svi) &
           STATE != "AK")

nrow(data_count %>% filter(party %in% c('Democratic', 'Republican')))
```

Children who engaged with the AFC prior to age 1
```{r}
ct = data_count %>% filter(years_to_engage < 1) %>%
  group_by(party) %>%
  summarize(n())

ct[ct$party == 'Democratic','n()'] + ct[ct$party == 'Republican','n()']
ct
```

Children born in or after 1988
```{r}
data_count = process_data(filename = 'child_politics_covariates_01202026_2018.csv.zip', 
                             time_var = 'time_to_vax', 
                             filter_yr = 1988, 
                             filter_outcome_time= Inf,
                             filter_engage_time = 1,
                             remove_after_4 = FALSE)
nrow(data_count %>% filter(party %in% c('Democratic', 'Republican')))
```

Children born in or after 2000
```{r}
data_count = process_data(filename = 'child_politics_covariates_01202026_2018.csv.zip', 
                             time_var = 'time_to_vax', 
                             filter_yr = 2000, 
                             filter_outcome_time= Inf,
                             filter_engage_time = 1,
                             remove_after_4 = FALSE)
nrow(data_count %>% filter(party %in% c('Democratic', 'Republican')))
```

## Data cleaning
```{r}
# outcome is 
data_vax_late = process_data(filename = 'child_politics_covariates_01202026_2018.csv.zip', 
                             time_var = 'time_to_vax', 
                             filter_yr = 1988, 
                             filter_outcome_time= 100,
                             filter_engage_time = 1,
                             remove_after_4 = FALSE)
```

```{r}
data <- data_vax_late %>%
  filter(indic == TRUE)
data$delay <- as.numeric(data$time_to_vax)-(16/12)
data$delay <- pmax(data$delay, 0)
data$delay <- as.numeric(data$delay)*365
nrow(data)
```

Plot the disparity in time to delay over time
```{r}
plot_year_disparity(data, outcome = 'delay', 
                    party_baseline = "D", 
                    title = "", 
                    hist_title = "Number of Observations per Year",
                    ylab = "Estimated Gap in Days of Delay",
                    line_color = "darkslategray4",
                    hist_color = "darkslategray4",
                    legend = FALSE)

ggsave(
  '~/afc-claire/code/figures/time_to_delay_2018.png',
  width = 6,
  height = 5)

ggsave(
  '~/afc-claire/code/figures/time_to_delay_2018.pdf',
  width = 6,
  height = 5)
```

Run the interaction model on time to delay
```{r}
sum(!is.na(data$svi))
model_table = interaction_model(data = data, ref_year = 1988, 
                                outcome = 'delay', party_reference = 'D', 
                                state_FE = FALSE, x = TRUE)
```

```{r}
rownames(model_table) <- NULL
# Generate LaTeX table with kable
latex_out <- kable(model_table, 
      format = "latex", 
      caption = "Delay", 
      booktabs = TRUE,  # For cleaner lines
      align = c("l"),
      escape = FALSE)  # Left-align the first column and right-align others
cat(latex_out)
```

# Run a second analysis without outliers (post-age-7)
Children with “in-time” first doses (received MMR vaccine at or after age 12 months and before age 6 years, 11 months) 
```{r}
data_no_outliers <- data %>%
  filter(time_to_vax < 6 + 11/12)
nrow(data_no_outliers)
```

```{r}
sum(!is.na(data_no_outliers$svi))
model_table = interaction_model(data = data_no_outliers, ref_year = 1988, 
                                outcome = 'delay', party_reference = 'D', 
                                state_FE = FALSE, x = TRUE)
```

```{r}
sum(!is.na(data_no_outliers$svi))
rownames(model_table) <- NULL
# Generate LaTeX table with kable
latex_out <- kable(model_table, 
      format = "latex", 
      caption = "Delay", 
      booktabs = TRUE,  # For cleaner lines
      align = c("l"),
      escape = FALSE)  # Left-align the first column and right-align others
cat(latex_out)
```