---
title: "05_robustness_check"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(broom)
library(dplyr)
library(splines)
library(purrr)
library(tidyr)
library(sandwich)
library(emmeans)
library(ggplot2)
library(fixest)
library(tidyr)
library(patchwork)
library(scales)
library(kableExtra)
library(stargazer)
library(lme4)
library(broom.mixed)  # For tidying lmer output
library(lmerTest)
library(knitr)
source('~/afc-claire/code/analysis/00_partisan_difference_functions.R')
```

## Refusal Indicator
```{r}
# outcome is whether a vaccine was received
data = process_data(filename = 'child_politics_refusals_covariates_01202026.csv.zip', 
                    time_var = 'time_to_refusal', 
                    filter_yr = 2000, 
                    filter_outcome_time = 7,
                    filter_engage_time = 1,
                    remove_after_4 = FALSE)

data$indic = as.numeric(data$indic)*100
data$year_num = as.numeric(data$year_num)
data = data %>%
  filter(parent_count <= 2)
```

Children with valid time to refusal (> 0) with one or two potential parents
```{r}
nrow(data)
sum(data$indic/100)
```

```{r}
model_table = interaction_model(data, party_reference = 'D',
                                ref_year = 2000, outcome = 'indic', 
                                state_FE = FALSE, x = TRUE)

sum(!is.na(data$svi))
sum(data[!is.na(data$svi), 'indic'])/100


rownames(model_table) <- NULL
# Generate LaTeX table with kable
latex_out <- kable(model_table, 
      format = "latex", 
      caption = "Robustness -- Refusal Indicator", 
      booktabs = TRUE,  # For cleaner lines
      align = c("l"),
      escape = FALSE)  # Left-align the first column and right-align others
cat(latex_out)
```



## MMR Vaccination Indicator
```{r}
# outcome is whether a vaccine was received
data = process_data(filename = 'child_politics_covariates_01202026.csv.zip', 
                             time_var = 'time_to_vax', 
                             filter_yr = 1988, 
                             filter_outcome_time= 3+11/12, # must have been vaccinated for an on time second dose
                             filter_engage_time = 1,
                             remove_after_4 = FALSE)
data$indic = as.numeric(data$indic)*100
data$year_num = as.numeric(data$year_num)
data = data %>%
  filter(parent_count <= 2)
```

Children born in or after 1988 with 1 or 2 potential parents:
Children with “on-track” first dose (received MMR vaccine at or after age 12 months and before age 3 years, 11 months) with 1 or 2 potential parents
```{r}
nrow(data)
sum(data$indic/100)
```

```{r}
model_table = interaction_model(data, party_reference = 'D', ref_year = 1988, outcome = 'indic', state_FE = FALSE, x = TRUE)

rownames(model_table) <- NULL

sum(!is.na(data$svi))
sum(data[!is.na(data$svi), 'indic'])/100

# Generate LaTeX table with kable
latex_out <- kable(model_table, 
      format = "latex", 
      caption = "Robustness -- Delay indicator", 
      booktabs = TRUE,  # For cleaner lines
      align = c("l"),
      escape = FALSE)  # Left-align the first column and right-align others
cat(latex_out)
```

## MMR Vaccination Indicator (12-15 months)
```{r}
# outcome is whether a vaccine was received
data = process_data(filename = 'child_politics_covariates_01202026.csv.zip', 
                             time_var = 'time_to_vax', 
                             filter_yr = 1988, 
                             filter_outcome_time= 16/12, # must have been vaccinated for an on time second dose
                             filter_engage_time = 1,
                             remove_after_4 = FALSE)
data$indic = as.numeric(data$indic)*100
data$year_num = as.numeric(data$year_num)
data = data %>%
  filter(parent_count <= 2)
```

```{r}
nrow(data)
sum(data$indic/100)
```

```{r}
model_table = interaction_model(data, party_reference = 'D', ref_year = 1988, outcome = 'indic', state_FE = FALSE, x = TRUE)

rownames(model_table) <- NULL
# Generate LaTeX table with kable
latex_out <- kable(model_table, 
      format = "latex", 
      caption = "Robustness -- Vaccination age 12-15", 
      booktabs = TRUE,  # For cleaner lines
      align = c("l"),
      escape = FALSE)  # Left-align the first column and right-align others
cat(latex_out)
```

## Time to delay
```{r}
# outcome is 
data_vax_late = process_data(filename = 'child_politics_covariates_01202026.csv.zip', 
                             time_var = 'time_to_vax', 
                             filter_yr = 1988, 
                             filter_outcome_time= 6+11/12,
                             filter_engage_time = 1,
                             remove_after_4 = FALSE)

data <- data_vax_late %>%
  filter(indic == TRUE)
data$delay <- as.numeric(data$time_to_vax)-(16/12)
data$delay <- pmax(data$delay, 0)
data$delay <- as.numeric(data$delay)*365
nrow(data)
data = data %>%
  filter(parent_count <= 2)
```

Children with “in-time” first doses (received MMR vaccine at or after age 12 months and before age 6 years, 11 months) with 1 or 2 potential parents:
```{r}
nrow(data)
```

```{r}
model_table = interaction_model(data = data, ref_year = 1988, 
                                outcome = 'delay', party_reference = 'D', 
                                state_FE = FALSE, x = TRUE)
rownames(model_table) <- NULL

sum(!is.na(data$svi))

# Generate LaTeX table with kable
latex_out <- kable(model_table, 
      format = "latex", 
      caption = "Robustness -- time to Delay", 
      booktabs = TRUE,  # For cleaner lines
      align = c("l"),
      escape = FALSE)  # Left-align the first column and right-align others
cat(latex_out)
```